---
title: "task2-aoxu"
author: "AO XU"
date: "2022-11-08"
output: html_document
---

Perform a secondary tokenization of the data to obtain bigrams. Fit a logistic principal component regression model to the word-tokenized data, and then input the predicted log-odds-ratios together with some number of principal components of the bigram-tokenized data to a second logistic regression model. Based on the results, does it seem like the bigrams capture additional information about the claims status of a page?

```{r}
# setup
library(tidyverse)
library(tidytext)
library(tokenizers)
library(textstem)
library(stopwords)
```


```{r}
load('/Users/xuao/Documents/2022Fall/Pstat197/claims-group-12/data/claims-raw.RData')
load('/Users/xuao/Documents/2022Fall/Pstat197/claims-group-12/data/claims-test.Rdata')
load('/Users/xuao/Documents/2022Fall/Pstat197/claims-group-12/data/claims-clean-example.Rdata')
```
```{r}
ls()
```
```{r}
# We change the preprocessing.r firstly and then use npl_fn2()
claims_bigrams <- claims_clean %>% 
  nlp_fn2()
```

```{r}
# partition data
library(tidymodels)
set.seed(198888)
partitions <- claims_bigrams %>% initial_split(prop = 0.8)
```

```{r}
# To separate DTM from labels, we set dtm and labels
testset_dtm <- testing(partitions) %>%
  select(-.id, -bclass)
testset_labels <- testing(partitions) %>%
  select(.id, bclass)
trainset_dtm <- training(partitions) %>%
  select(-.id, -bclass)
trainset_labels <- training(partitions) %>%
  select(.id, bclass)
```










